Word learning at the semantics pragmatics interface

### 2020-04-08 paper/supplementary_material.Rmd
edits until mixture model math in explanation section

In this section we explore how we can best explain information integration across development. We explore alternative ways to think about information integration. The *integration model* outlined above operates via Bayesian inference in that the prior probability of a referent - a consequence of the common ground manipulation - is updated upon hearing the utterance and computing the mutual exclusivity inference. In essence, this model is a multiplicative model because the probability of each referent is proportional to the product of the likelihood and the prior. The alternative model we consider here is an additive model. This *mixture model* assumes that the two inferences are computed separately and then weighted by some ratio $\phi$. Psychologically, $\phi$ may be interpreted as a bias for one type of inference relative to the other.

With respect to developmental change, the *integration model* assumes that the process by which information is integrated remains the same across development. What changes is children's semantic knowledge, their expectations about speaker informativeness and their sensitivity to common ground. But the way these information sources are combined remains the same across age. As an alternative, we explore a *developmental mixture model*. This model makes the same assumptions about developmental change in the individual information sources but, in addition, also assumes that the way that the the mutual exclusivity and the common ground inference are combined with one another changes over time. It is structurally identical to the *mixture model* but the mixture parameter $\phi$ is a function of age.

In this section, we make use of all the available data. We use the data from experiment 1 and 2 to compute prior distributions over model parameters which are subsequently updated depending on how well the model predictions they generate fit the data.

@@

The *integration model* in this section differs from the same model in the prediction section only in the distributions for the parameters representing the different information sources. Figure \@ref(fig:figa1) - \@ref(fig:figa3) in the appendix show how the  parameter distributions differ between the prediction and the explanation version of the *integration* model. As a quick summary, we can say that semantic knowledge and speaker informativeness have similar distributions when taking into account all the data compared to when estimating these parameters only based on experiment 1 and 2. In contrast, the intercept for common ground sensitivity is estimated to be larger and the slope shallower. The code to run the model can be found in the associated online repository (file: xxxxxxx). Figure \@ref(fig:fig9) shows model predictions for the *integration model* in comparison to the data from experiment 3.

@@

In the *mixture model* the two inferences are computed in the same way as in in the *integration model*. Subsequently, they are weighted by the mixture parameter $\phi$:

>>>>

In this section we explore how we can best explain information integration across development. We explore alternative ways to think about information integration. The *integration model* outlined above operates via Bayesian inference in that the prior probability of a referent (a consequence of the common ground manipulation) is updated via the likelihood of hearing the utterance heard from a speaker, which is used to derive the mutual exclusivity inference. In essence, this model is a multiplicative model because the posterior probability of each referent given the utterance is proportional to the product of the likelihood of a speaker saying that utterance and the prior probability of that referent.

Information sources need not be integrated in a Bayesian manner. Rather than be part of the same pragmatic reasoning architecture, the common ground and mutual exclusitivity inferences we consider could be computed separately and then combined. A listener could integrate these two independent inferences in an additive manner, weighting the sources of information by some ratio $\phi$. $\phi$ is then a bias to prefer one type of inference relative to the other. We formalize this alternative hypothesis as a  *mixture model*.

The *integration* and *mixture* models have different implications for developmental change.
The *integration model* assumes that the process by which information is integrated remains constant across development. What changes is children's semantic knowledge, their expectations about speaker informativeness, and their sensitivity to common ground, but the way these information sources are combined remains the same across age. The *mixture model* alternatively posits that there is some bias or preference for one information source, and this bias could across development. This *developmental mixture model*  makes the same assumptions about developmental change in the individual information sources as the *integration model* but, in addition, assumes that the way that the the mutual exclusivity and the common ground inference are combined with one another changes over time. This model is structurally identical to the *mixture model* but the mixture parameter $\phi$ is a function of age.

In this section, we make use of all the available data to arbitrate between these alternative models (a fully Bayesian analysis). As before, Experiments 1 and 2 directly constrain the parameters governing semantic knowledge, speaker informativeness, and the prior distribution over referents (via common ground; Expt. 2). Now, in addition, we incorporate the data from Experiment 3 to additionally constrain these parameters as well as inform the mixture parameter for the mixture model.

@@

The *integration model* in this section differs from the integration model in the **Prediction Section** only in that the parameter distributions are now additionally informed by the data from Experiment 3. Figure \@ref(fig:figa1) - \@ref(fig:figa3) in the Appendix show how the parameter distributions differ between the prediction and the explanation version of the *integration* model. Semantic knowledge and speaker informativeness have similar posterior distributions when taking into account all the data compared to when estimating these parameters only based on experiment 1 and 2. In contrast, the intercept for common ground sensitivity is estimated to be larger and the slope shallower after taking into account Experiment 3 data. That is, our best guess for common ground sensitivity after taking into account the data from Experiment 3 is that children overall are more sensitive to the common ground manipulation and there is less developmental change. The code to run the model can be found in the associated online repository (file: xxxxxxx). Figure \@ref(fig:fig9) shows model predictions for the *integration model* in comparison to the data from experiment 3.

@@

In the *mixture model* the two inferences (common ground and mutual exclusivity) are computed in the same way as in in the *integration model*. Subsequently, they are weighted by the mixture parameter $\phi$:
